Multi-level modeling with Openflexo/\FML

### 2022-02-24 1-main.tex
comment useless packages
comment useless font

\usepackage{multirow}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
%\usepackage{tikz-uml}
%\usepackage{float}
\usepackage{algorithmic,algorithm}

@@

\DeclareTextFontCommand{\mytexttt}{\ttfamily\hyphenchar\font=45\relax}

@@

\hypersetup{
  pdfauthor={Sylvain Guérin, Joel Champeau, Jean-Christophe Bach, Antoine
  Beugnard, Fabien Dagnat, Salvador Martinez},
  pdftitle={Multi-level modeling with Openflexo/\FML -- A contribution to the \mlpc},
  bookmarks=true,
  unicode=true,
  pdfpagelabels=true,
  pdfkeywords={Multi-Level Modeling Challenge, Federation Modeling Language,
  Openflexo},
  %abstract
  pdfsubject={Model federation is a multi-model \emph{management} approach based on the use of virtual models and loosely coupled links. The models in a federation remain autonomous and represented in their original technological spaces whereas virtual models and links (which are not level bounded) serve as control components used to present different views to the users and  maintain synchronization. In this paper we tackle the \emph{MULTI process modeling challenge}, which consists in providing a solution to the problem of specifying and enacting processes. Solutions must fulfill a number of requirements for a process representation defined at an abstract process-definition level and at various more concrete domain-specific levels, resulting in a multi-level hierarchy of related models. We present a solution based on model federation and discuss the advantages and limitations of using this approach for multi-level modeling. Concretely, we use virtual models and more precisely the Federation Modeling Language ({FML}) that serves to describe them as the main building block in order to solve the process modeling challenge whereas the federation aspect is used as a means to provide editing tooling for the resulting process language. Our solution is fully implemented with the Openflexo framework. It fulfills all the challenge requirements.
}
}

@@

\section{Introduction}
\label{sec:introduction}
\input{3-introduction.tex}

@@

\section{Technology}
\label{sec:technology}
\input{4-technology.tex}

\section{Analysis}
\label{sec:analysis}
\input{5-analysis.tex}

\section{Model presentation}
\label{sec:model}
\input{6-modelpresentation.tex}

\section{Satisfaction of requirements}
\label{sec:requirements}
\input{7-requirementssatisfaction.tex}

\section{Assessment of the modeling solution}
\label{sec:discussion}
\input{8-discussion.tex}

\section{Related work}
\label{sec:relatedwork}
\input{9-relatedworks.tex}

\section{Conclusions}
\label{sec:conclusions}
\input{10-conclusions.tex}

>>>>

\usepackage{bookmark}
\usepackage{multirow}
\usepackage{listings}
%\usepackage{xcolor}
%\usepackage{hyperref}
%\usepackage{tikz-uml}
%\usepackage{float}
%\usepackage{algorithmic,algorithm}

@@

%\DeclareTextFontCommand{\mytexttt}{\ttfamily\hyphenchar\font=45\relax}

@@

\hypersetup{
  pdfauthor={Sylvain Guérin, Joel Champeau, Jean-Christophe Bach, Antoine
  Beugnard, Fabien Dagnat, Salvador Martinez},
  pdftitle={Multi-level modeling with Openflexo/\FML -- A contribution to the \mlpc},
  unicode=true,
  pdfkeywords={Multi-Level Modeling Challenge, Federation Modeling Language,
  Openflexo},
  %abstract
  pdfsubject={Model federation is a multi-model \emph{management} approach based on the use of virtual models and loosely coupled links. The models in a federation remain autonomous and represented in their original technological spaces whereas virtual models and links (which are not level bounded) serve as control components used to present different views to the users and  maintain synchronization. In this paper we tackle the \emph{MULTI process modeling challenge}, which consists in providing a solution to the problem of specifying and enacting processes. Solutions must fulfill a number of requirements for a process representation defined at an abstract process-definition level and at various more concrete domain-specific levels, resulting in a multi-level hierarchy of related models. We present a solution based on model federation and discuss the advantages and limitations of using this approach for multi-level modeling. Concretely, we use virtual models and more precisely the Federation Modeling Language ({FML}) that serves to describe them as the main building block in order to solve the process modeling challenge whereas the federation aspect is used as a means to provide editing tooling for the resulting process language. Our solution is fully implemented with the Openflexo framework. It fulfills all the challenge requirements.
}
}

@@

\section{Introduction}
\label{sec:introduction}
\pdfbookmark[section]{Introduction}{sec:introduction}
\input{3-introduction.tex}

@@

\section{Technology}
\label{sec:technology}
\pdfbookmark[section]{Technology}{sec:technology}
\input{4-technology.tex}

\section{Analysis}
\label{sec:analysis}
\pdfbookmark[section]{Analysis}{sec:analysis}
\input{5-analysis.tex}

\section{Model presentation}
\label{sec:model}
\pdfbookmark[section]{Model presentation}{sec:model}
\input{6-modelpresentation.tex}

\section{Satisfaction of requirements}
\label{sec:requirements}
\pdfbookmark[section]{Satisfaction of requirements}{sec:requirements}
\input{7-requirementssatisfaction.tex}

\section{Assessment of the modeling solution}
\label{sec:discussion}
\pdfbookmark[section]{Assessment of the modeling solution}{sec:discussion}
\input{8-discussion.tex}

\section{Related work}
\label{sec:relatedwork}
\pdfbookmark[section]{Related work}{sec:relatedwork}
\input{9-relatedworks.tex}

\section{Conclusions}
\label{sec:conclusions}
\pdfbookmark[section]{Conclusions}{sec:conclusions}
\input{10-conclusions.tex}
